Gravitational Lens Modelling of Flux Ratio Anomalous System B1555+375

### 2015-04-21 papers/B1555_EdgeOn/B1555_letter.tex
update 2-SIE paras in text
Small addition to B1555 discussion

\begin{table}
% \centering
% \begin{minipage}{140mm}
  \caption{Best-fit parameters of B1555+375 lens model.}
  \begin{tabular}{@{}ccc}
\hline 
 Parameter  & \multicolumn{2}{c}{Lens model} \\
		&SIE+expdisk& 2-SIE		   
\\
\hline
$x_1$  	  & $-0.1883$	& $-0.1809$  \\
$y_1$	  &$-0.1923$	&$-0.1702$  \\
$x_2$	  &$-0.1615$ 	&$-0.1592$  \\
$y_2$	  &$-0.2502$	& $-0.1833$  \\
$\sigma_1$ &$141.3$     & $144.6$ \\
$e_1$	  & $0.27$	& $0.27$ \\
$\theta_1$ &$105.5 \degr$ & $97.7 \degr$ \\
$M_{tot,2}$  & $3.59\times 10^{10} $  & ...	 \\  
$\sigma_2$ & ...        &$123.8$ \\  
$e_2$	  &$0.84$	&$0.83$  \\
$\theta_2$ &$7.4\degr$ &$7.4\degr$  \\
$r_e$	  & $0.20 ''$ &  ... \\
\hline
\end{tabular}

@@

Component	&\multicolumn{2}{c}{MERLIN} 	 & \multicolumn{4}{c}{Model} \\
					&\multicolumn{2}{c}{5 GHz}		&	\multicolumn{2}{c}{SIE+expdisk} &\multicolumn{2}{c}{ 2-SIE}		\\
					 &East &North &East 		&North &East 		&North\\ 
\hline
A ........ &$0$    		&$0$		&$0.0000$ &$0.0000$   &   $0.0000$   &  $ 0.0000$\\  
B ........ &$-0.0726$ 	&$+0.0480$	&$-0.0726$ &$+0.0479$ & $-0.0726 $  &  $+0.0480$  \\  
C ........ &$-0.4117$  &$-0.0280$	&$-0.4117$ &$-0.0280$  & $-0.4117 $  &   $+0.0280$ \\  
D ........ &$-0.1619$  &$-0.3680$	&$-0.1609$ &$-0.3678$  & $-0.1618$    &  $+0.3680$ \\  
\hline
\end{tabular}

@@

>>>>

\begin{table}
% \centering
% \begin{minipage}{140mm}
  \caption{Best-fit parameters of B1555+375 lens model.}
  \begin{tabular}{@{}ccc}
\hline 
 Parameter  & \multicolumn{2}{c}{Lens model} \\
		&SIE+expdisk& 2-SIE		   
\\
\hline
$x_1$  	  & $-0.1883$	& $-0.1813$  \\
$y_1$	  &$-0.1923$	&$-0.1695$  \\
$x_2$	  &$-0.1615$ 	&$-0.1593$  \\
$y_2$	  &$-0.2502$	& $-0.1843$  \\
$\sigma_1$ &$141.3$     & $144.9$ \\
$e_1$	  & $0.27$	& $0.27$ \\
$\theta_1$ &$105.5 \degr$ & $97.7 \degr$ \\
$M_{tot,2}$  & $3.59\times 10^{10} $  & ...	 \\  
$\sigma_2$ & ...        &$123.5$ \\  
$e_2$	  &$0.84$	&$0.83$  \\
$\theta_2$ &$7.4\degr$ &$7.4\degr$  \\
$r_e$	  & $0.20 ''$ &  ... \\
\hline
\end{tabular}

@@

Component	&\multicolumn{2}{c}{MERLIN} 	 & \multicolumn{4}{c}{Model} \\
					&\multicolumn{2}{c}{5 GHz}		&	\multicolumn{2}{c}{SIE+expdisk} &\multicolumn{2}{c}{ 2-SIE}		\\
					 &East &North &East 		&North &East 		&North\\ 
\hline
A ........ &$0$    		&$0$		&$0.0000$ &$0.0000$   &   $0.0000$   &  $ 0.0000$\\  
B ........ &$-0.0726$ 	&$+0.0480$	&$-0.0726$ &$+0.0479$ & $-0.0726 $  &  $+0.0481$  \\  
C ........ &$-0.4117$  &$-0.0280$	&$-0.4117$ &$-0.0280$  & $-0.4117 $  &   $+0.0280$ \\  
D ........ &$-0.1619$  &$-0.3680$	&$-0.1610$ &$-0.3678$  & $-0.1620$    &  $+0.3682$ \\  
\hline
\end{tabular}

@@

Gravitational lensing is [one of] the most powerful methods for
studying substructure in galaxies outside of the Local Universe, and
the flux ratio anomaly systems are a key aspect of these
investigations.  However, before using the flux ratio anomaly in any
given system to investigate structure formation and the properties of
dark matter, it is critical to eliminate other possible explanations
for the difference between the observed and expected fluxes.  It
is for this reason that much of the effort in the flux-ratio technique
has been focused on radio-loud lens systems.  At these wavelengths,
dust extinction and microlensing effects should be minimal (although
see Koopmans et al. ?? for a rare example of radio microlensing).
Radio propagation effects can  affect radio fluxes, as is clearly
shown in the B0128 system [REF??].  However, these propagation effects
can be disentangled from substructure lensing because they have well
known dependencies on wavelength. [COMMENTS ABOUT B1555 AND OTHER
RADIO-LOUD SYSTEMS].
